% 
\IfFileExists{/u/r/dw580/Qspace/mypreamble}{ \input{/u/r/dw580/Qspace/mypreamble} }{ \input{/home/waalge/Qspace/mypreamble} } % Work and Laptop versions


\title{Future directions of research}
\author{Laura}
\date{}

\begin{document} 
\maketitle

Structure: Higgs bundles, branes, Applications. 

$\Sigma$ will be a compact Riemann surface of genus $g \geq 2$ 
$K = T^* \Sigma$


$(E, \varphi)$ Higgs bundles 


Remark : 
One can consider principal $G_\mathbb{C} $ - Higgs bundles.
For $ G_\mathbb{C} < \mathrm{GL}_n \mathbb{C} $ we take classical $(E, \varphi)$ and extend 
conditions reflecting the structure of the group.

For eaxple $ \mathrm{SL}_m \mathbb{C}  $ , then $E = \Lambda^m E \cong \mathcal{O} $ 
$ \mathrm{Tr} (\varphi) $ 

If $ G_\mathbb{C}  = \mathrm{Sp}_{2m} \mathbb{C}  $ then require symplectic 
and $ \omega ( \varphi ???, w)  = \omega ( v, \varphi w) $ compatibility cond. 

$\mathcal{M} _{G} $ be the moduli space of $ G$-Higgs bundles. 

Have that $ \mathcal{M} _G $ is a hyperkahler structure.
We inherit complex structure from $\Sigma$ and denot it $I$,
we inherit complex structure from $ G_\mathbb{C} $ and denote it $J$. 
Together these generate the hyperkahler structure. 
Have the holomorphic symplectic structures $\Omega _i $. 

A Lagrangian subspace with respect to a holomorphic symplectic strutcure for an A-brane. 
A complex submanifold with respect to a complex structure is a B-brane.

Remark: We can then ask for, for example $(A, B, B)$, that is an A-brane wrt $\Omega_I$, and $B$ brane wrt $??$

Question: How to construct families of these branes.

We have the correspondence between $ \mathcal{M} _{G_\mathbb{C}  } $ and $\mathrm{Red} ^+ (\pi_1 (\Sigma) \rightarrow G_\mathbb{C} ) / \sim $ 
What do branes correspond to in this space?
Similarly, with $ \mathcal{A}_{G_\mathbb{C} } $ 

Remark: 
Given $ G_\mathbb{C}  $ there is a Langlands dual group. 
\begin{align}
    [[LIST OF DUAL GROUPS ]]
    GL & GL 
    SL & PGL 
    SP & SO (2m+1 ) 
    SO & SO 
\end{align}

Let $ G_\mathbb{C} ^L $ denote the Langlands dual. 
Mirror symmetry SYZ 
$\mathcal{M} _{G_\mathbb{C}  ^L } \rightarrow \mathcal{A} _{G_\mathbb{C}  ^L } $ 
and there is isom $\mathcal{A} _{G_\mathbb{C}  } \cong \mathcal{A} _{G_\mathbb{C}  ^L } $ 

Refrences : 
02 
06 
07 
Hitchin 

Question: 
What are dual branes across a mirror symmetry correspondence. 

Remark: 
\begin{align}
    \mathcal{M} _ {G_\mathbb{C} } & \mathcal{M} _ {G_\mathbb{C} ^L } \\
    (B, A, A) & (B,B,B) \\
    (A, B, A) & (A,B,A) \\
    [[ OTHERES ]] 
\end{align}

Question: A new space such that all branes are of self dual type?
In string theory appear branes appear as boundary conditions that come in pairs, 
that are often self dual. 

Suppose we endow $\Sigma $ with real structure given locally by conjugation.
Simultaneously consider antiholomorphic involtuion fixing $G$ in $G_\mathbb{C} $. 
Ie involution fixing maximal compact subgroup. 

$( E, \varphi) \rightarrow (fg(E), -fg(\varphi)) $ 
this is an involution that fixes $(A,B,A)$ -brane.

Hitchin 92, considering real Higgs bundles.
Kupuscin and Witten later 96 saw fixes $(B,A,A)$ branes. 


[[ COMMUTATIVE DIAGRAM WITH ALL MODULI SPACES  ]] 

Conjecture: 
The dual $(A,B,A)$ brane in the moduli space $ \mathcal{M}_{G_\mathbb{C}  ^L} $ 
is the one fixed by involution induced.

\begin{theorem}
...
\end{theorem}

Given a 3 manifold for which $ \partial M = \Sigma$. 
Which representations of $ \pi_1 ( \Sigma) $ extend to $ \pi_1 (M)$.
Relates to knots on $S^3$. 

Let $ M = \Sigma \times [-1, 1] /\sim  $ where $ (x,t) \sim (f(x) , -t) $. 

\begin{theorem}
    The fixed... (aba)-branes 
    for which ... 
\end{theorem}



\bibliographystyle{plain}
\bibliography{}


\end{document} 

