
% 
\input{preamble}


\title{P=W conjecture}
\author{}
\date{}

\begin{document} 
\maketitle

$\Sigma$ is a Riemann surface with genus $g \geq 2 $ 
Let $ n >0 $ and $ d \in \mathbb{Z} $ and $ \mathrm{gcd} =1 $. 

\begin{align}
    \mathcal{M}_{\mathrm{betti}} \rightarrow  Mdol
\end{align}

\begin{align}
    Mbetti \{ A_i, B_i \in GLnC , i = 1, \dots, g | \pi[A_i, B_i ] = \xi ^d_n I_n \} // GLn\mathbb{C} 
\end{align}

\begin{align}
    Mdol = stable higgs bundles of rk n and degree d 
\end{align}

NAHT implies 
$ H^* ( Mbetti) = H^* Mdol$ 
Want to see he difference on the level of coholomogy groups

How? Mixed hodge structures. 

\section{Sheaf cohomologies} % (fold)

\begin{definition}
Let $X$ be a complex algebraic variety. 
    $\mathcal{D} _{C}  ^b (X) $ is the derived category of constructible sheaves. 

    The objects are complexes of sheaves of abelian groups 
    such that their cohomologies are constructable. 
    That is for a given chain there exists a stratification such that ...


    The morphisms are chain maps, modulo null-homotopic ones and invert quasi isomorphism. 
\end{definition}

$ E_p \in dcat $ gives rise to $ H ^* ( X, E_\bullet ) $ 
Choose $ E_\bullet = I _\bullet $ 
and $I$ such taht $ I_i $ are injective objects. 
and apply $\Gamma ( X, I_\bullet) $ 
$ H ^i ( X, E_\bullet ) := H^i ( \Gamma ( X, I_\bullet) ) $ 

FOr instance if we have a finite filtration 
\begin{equation}
    E_\bullet ^{1} \rightarrow     
    E_\bullet ^{2} \rightarrow     
    \dots 
    \bigcup_ i E_\bullet ^{i}  = E_\bullet 
\end{equation}
It induces a filtration at the level of homology groups $H^* ( X, E_\bullet) $. 

% section (end)



\section{W} % (fold)

Recall from usual Hodge theory we know that $ \mathbb{C} \cong \Omega_X ^* $ (analytic). 
Thus $H^*(X, \mathbb{C} ) \cong H^* ( X, \Omega_X ^* ) $ 

$\Omega_X ^ * $ admits a stupid filtration 
\begin{equation}
    (F^i \Omega_X ^* ) = \begin{cases} 
        0 & n<p \\
        \Omega_X ^n & n \geq p 
    \end{cases} 
\end{equation}

Hodge: If $ X$ is a Kahler and compact, then: 
\begin{align}
    H^n ( X, \mathbb{C} ) \cong \bigoplus_{p+q = n } = H^{p,q} ( X, \mathbb{C} ) 
\end{align}
and $ H^{p,q} ( X) \cong \overline{ H^{q,p} ( X) } $  

Let us suppose that $ X$ is not compact, but smooth. 
and we have a compactification $ X \rightarrow \bar{X} $ 
and $Y \subset \bar{X} $ is the complement set. 
It is a collection of divisors on $\bar{X} $ 

On $ \bar{X} $ we can define meromorphic 1-forms,
locally modelled on $ dz_i/z_i $ where $ Y = \bigcap Y_i $. 
Want divisor to have at worst normal crossings 

\begin{definition}
    \begin{align}
        \Omega_X ^ 1 \left< Y \right> = \{ sheaf of 1-forms generated by \Omega_X ^1 and dz_i / z_i \}
        \Omega_X ^p = \Lambda ^p ( \Omega_X ^1 ) 
    \end{align}


\end{definition}

Fact 
\begin{align}
    H^*  ( X, \mathbb{C}  ) = H^*  ( ...) 
\end{align}

\begin{definition}
    $W_n ( \Omega_\bar{X} ^p \left<Y \right> ) := \left< \alpha \wedge dz_{i_1} / z_{i_1} ... \right> $ 
    weighted filtration. 
\end{definition}

Now we have two filtration on $H^* ( X, \mathbb{C} ) $: $ W_\bullet $ is increasing, $ F^\bullet $ is decreasing. 

\begin{theorem}
    (Deligne)  Let $ X $ be an algebraic variety over $ \mathbb{C} $. 
    In every cohomological degree $n$, 
    the graded piece $ \mathrm{Gr}_L ^W := W_L / W_{L-1 } $ 
    admits a canonical decomposition 
    \begin{align}
        GRLW = \bigoplus GRPF (GRLW) , ~~ GRFP \ong \overline{GRFL-P}
    \end{align}
\end{theorem}

$H^2 = H^{2,0} \oplus H^{1,1} \oplus H^{0,2} $ 
grading gives map $ H^2 \rightarrow   H^2 _{(2) } \oplus  H^2 _{(2) }\oplus   H^2 _{(2) } $ 
No longer have `pure hodge' decomposition. 
have a filtrated. 

Properties:
$ W_\bullet $ and $ F^\bullet $ commute with pullbacks. 
Compatible with Kunneth cup product. 
On $H^j $, $ W $ has non-zero degrees. 
$[j, z_j ] $ is $ X $ is smooth non-compact. 
$[ 0, j ] $ if $ X $ is singular compact.
$[ j ] $ if $ X $ is  smooth compact. 
$[ 0, 2j ] $ in general. 

Non abelian hodge theory in rank 1. 

$ Mbetti = ( \mathbb{C} ^* ) ^{2g} \rightarrow  \mathrm{Jac} _\Sigma \times \mathbb{C}  ^g = Mdol $ 

$H^* ( Mbetti) = H^* ( \mathbb{C} ^* ) ^{\otimes 2g} $ 

$ H^*( \mathbb{C} ^* ) = \mathbb{C} \oplus \mathbb{C}  $ 
cohomology degree (0,1) 
Weight $( 0, 2) $. 

On the side of $Mdol$ the weight filtration is trivial. 

So question is what happens if the filtration is carried across. 
The answer comes in the form of perverse sheaves.... 

Hitchin-Base  $\mathcal{B} $ 
\begin{align}
    Mdol \rightarrow  \mathcal{B} 
\end{align}

Have 
\begin{align}
     H^* ( Mdol , \mathbb{C} ) \cong H^* ( \mathcal{B} , \pi_* \underline{\mathbb{C} } ) 
\end{align}
taking the stupid filtration. 
Gives leray filtration, and this is not the right one!! 

Instead take the category inside perverse sheaves... 

The conjecture: 
Under natural diffeomorphism 
$Mdol \cong Mbetti $ then $ P= W $ 
Low rank cases dealt wit h 
% section (end)




\bibliographystyle{plain}
\bibliography{}


\end{document} 

