% 
\IfFileExists{/u/r/dw580/Qspace/mypreamble}{ \input{/u/r/dw580/Qspace/mypreamble} }{ \input{/home/waalge/Qspace/mypreamble} } % Work and Laptop versions


\title{Extending to non compact Riemann surfaces}
\author{}
\date{}

\begin{document} 
\maketitle
Non-abelian hodge theory for non compact curves (tame or wild) .

Have a punctured Rieman surface $ X \setminus \{ p_1 , \dtos, p_k \} $ 

Recap the compact case : 
1) Harmonic Bundle, 
2) flat (stable) complex bundle, 
3) Irreducible representations $ \pi_1(X) \rightarrow GLn $ 
4) Higgs bundles 

Maps: 
1) ---> 2)
2) ---> 1) Couvette donladson 
2) ---> 3) RH 
1) ---> 4) << Hitchn Kobeshi 


Maps from moduli ...

Over the top have the non-compact analogues that we'll see. 
Includes parabolic bundles, 
parabolic Higgs bundle 

\begin{definition}
    A parabolic bundle $ E \rightarrow \bar{X} $ over compact Riemann surface $ \bar{X}$ 
    is a bundle together with a subset $ D \subset \bar{X}$, 
    such that for each $p \in D$, we have a full flag 
    \begin{align}
        E|_p > E|_{1,p} > \dots > E|_{r , p } > \{ 0 \} \\
        0 \leq \alpha_ 1 < \dots < \alpha _r < 1
    \end{align}
\end{definition}

This models holomorphic bundles on $X$. 

Parabolic Higgs field $(E, E_\alpha , \vartheta) $ 
such that $ E_{\alpha , p } \rightarrow \Omega_X \otimes E_{\alpha, p} $ .

Parabolic flat bundle $(E, \{ E_\alpha \}, \nabla ) $ 
around the punctures we model these in local coordinates $ \frac{dz}{z} $ weigthed by alpha. 

Both $ \vartheta $ and $\nabla $ allow poles of order at most one. 

Stability for parabolic Higgs-bundle. 

\begin{definition}
    Let $ ( E, \{ E_\alpha \} $ parabolic bundle. 
    For subbundle $F \rightarrow  E $ we inherit the flag structure by restricting the flags $\{E_\alpha\} $.

    $\mathrm{pardeg}(E) = \mathrm{deg}(E) + \sum_p \sum_i \alpha_i(p) $. 
    
    Then $E$ is stable if it admits the stability where we consider the the $\mathrm{pardeg} $ instead of $\mathrm{deg}$ 
\end{definition}

\begin{definition}
    $(E, D, D'', h) $ is tame  if 
    for each puncture  the standard metric on $D^2$ 
    1) Higgs bundles side $ | \lambda_i | _{D_z} < c / |z| $ 
    2) Flat bundle $ \nabla $ flat connection have at most polynomial growth at $p $
    $v$ my flat section then $ |v|^2 < r ^2 $ 

    As expressed in local coordinates
\end{definition}

We have a Riemann Hilbert singularieties. 
for connections with regular singularieties 

\begin{align}
    \mathrm{Rep} \{ \pi_1 ( \bar{X} \setminus D ) \rightarrow GLnC \} \rightarrow \{ \mbox{ flat connections with regular singularities} \} 
\end{align}

Tabulate 
$( E,\vartheta) $, $ (E, \nabla ) $ , $ (L, \mu) $ 

weights 

eigenvalues 



Moduli spaces

Once we fix the weight $\alpha$
recover all the results we want. 

$m \alpha $ hyperkaheler 

$Mbetti $ is the usual 
$Mdr$ has log connections 
$Mdol $ If we consider the special case of nilpotent Higgs fields 
$\vartheta = \begin{array} 0 &  * \\ 0 & 0 \end{array} $ 
    then $E_{i, p} \rightarrow E_{i+1, p } \otimes _p \Omega^1 _ X $ 

    Then consider the strong parabolic endomorphism. 


    What about the wild case??

    $ \nabla = \sum A_i z^{-i } dz $ 
    
    (Boalch - Biquard ) 

    Still get a correspondence 

    But we dont get Mbetti



\bibliographystyle{plain}
\bibliography{}


\end{document} 

