% 
\input{preamble}

\title{Stability of Higgs Bundles}
\author{Juultje Kok}
\date{}

\begin{document} 
\maketitle

\begin{definition}
    Let $M$ compact Riemann surface. 
    A $\mathrm{GL}_n $-Higgs bundle is pair $(V, \varphi)$ 
    where $ V$ is a holomorphic rank $n$ vector bundle and 
    $ \varphi$ is a holomorphic section of $ \mathrm{End}(V) \otimes K $.
    That is $ \varphi \in H^0 ( \mathrm{End} (V) \otimes K) $.
\end{definition}

\begin{definition}
    Say two Higgs bundles $(V, \varphi) $ and $(V', \varphi')$ are isomorphic if 
    there exists $ \psi: V \rightarrow  V'$ inducing the commutative diagram
    
    [[ DIAGRAMME ]] 
\end{definition}

Recall that for $P$ a principal $G$-bundle, 
say that connection $A$ on $P$, 
and $ \varphi \in \omega^1 ( M , \mathrm{ad} ( P) \otimes \mathbb{C} ) $ 
solve the Hitchin equations if $ F_ A = [ \varphi , \varphi ^* ] $ and $ \bar{\partial} _A \varphi = 0 $.

[[SIGN CONVENTION? / A THE CONNECTION OF THE ADJOINT?? ]] 

Claim: $ V = (P \otimes \mathbb{C} ^n) / G $ then $(V, \varphi) $ is a Higgs bundle. 
Note that $ \Omega^1 ( M, \mathrm{ad} ( P) \otimes \mathbb{C}  = H^0 ( M , ( \mathrm{ad} P \otimes \mathbb{C} ) \otimes K) $

Commutative diagram defining that map 
\begin{align}
    (\mathrm{ad}P \otimes \mathbb{C} )_x & \rightarrow  \mathrm{End}(V) _x \\
    [p, m ] & \mapsto ([pg, v] \mapsto [pg, g^{-1} m g v] ) 
\end{align}


\section{Stability} % (fold)

\begin{definition}
    Let $( V, \varphi) $ be Higgs bundle. 
    Say $ E \subset L$ is $ \varphi$ invariant if $ \varphi(E) \subset E \otimes K$. 
    In such cases, say $E$ is a Higgs subbundle. 

    A Higgs bundle is stable if $\mu(E) < \mu(V) $ for all Higgs subbundles. 
    Recall slope $ \mu(E) : = \mathrm{deg} ( \mathrm{det}(E)) / \mathrm{rank}(E) $ 
\end{definition}

Example: $(V,0)$ is stable if and only if $ V$ is stable as a vector bundle. 
In fact, if $ V$ is stable then any $\varphi$ gives rise to stable Higgs bundle. 
Furthermore, if $(V, \varphi)$ and $(V, \varphi') $ are isomorphic, then $ \varphi = \varphi'$.

\begin{align}
    \mathcal{M}_{\mathrm{Higgs}} \subset \{ ( V,\varphi) | \mbox{ $V$ stable} \} \rightarrow T^* \mathcal{M}_{\mathrm{Vect}} \\
    ( V, \varphi) \mapsto \varphi 
\end{align}

There is a 1-1 correspondence between self dual  Hitchin Pair $(F_A , E) $ upto Gauge 
and (semi?) stable Higgs bundles up to isomorphism 

Example: 

Let $ G = \mathrm{SU}(2) $. 
Then 
\begin{equation}
    \mathfrak{su}(2) \otimes \mathbb{C}  \cong \mathfrak{sl}(2, \mathbb{C} ) = \{ m \in \mathrm{Mat}(2, \mathbb{C} )| ~ \mathrm{tr}(m) = 0 \}
\end{equation}
$ \varphi \in H^0 ( \mathrm{End} _0 ( V) \otimes K) $ 
$V$ of rank 2. 

Remark: 
\begin{align}
    \mathrm{Hom} ( L_1 , L_2 ) \rightarrow  H^0 ( L_1 ^* \otimes L_2 ) 
\end{align}

[[ ISOM?? ]] 

$M = \mathbb{P} ^1 $, $V = \mathcal{O} (m) \oplus \mathcal{O} (n) $ , $K = \mathcal{O}(-2) $. 
Let $ \varphi: \mathcal{O} ( m) \oplus \mathcal{O} ( n) \rightarrow  \mathcal{O} (m -2) \oplus \mathcal{O} (n-2) $ 
then may regard $\varphi $ as a matrix with elements forms in the relevant bundles. 

Then $ \mathrm{det}(\mathcal{O} ( m) \oplus \mathcal{O} (n) = \mathcal{O} (m+n) $
As $ \mathrm{deg}( \mathcal{O} (m) = m $, there are no stable Higgs bundles in $\mathbb{P} ^1$. 

% section (end)

\section{Moduli} % (fold)


\begin{proposition}
If $V$ is unstable vector bundle of rank 2, 
then there exists a unique $L \subset V$ such that
$ \mathrm{deg}(L) \geq \frac{1}{2} \mathrm{deg} (\Lambda^2 V ) $ 
\begin{equation}
    0 \rightarrow  L \rightarrow V \rightarrow  L^* \otimes \mathrm{det} (V) \otimes 0 
\end{equation}
\end{proposition}

\begin{proposition}
    Let $ g>1 $. A rank $2$ vector bundle $V$ occurs in a stable Higgs bundle $(V, \varphi) $ if and only if one of the following holds: 
    \begin{enumerate}[label=(\roman*)]
        \item $V$ is stable,
        \item $V$ is semistable and $g>2$, 
        \item $V$ is semistable and $g=2$, and $V = U \otimes L$, 
            and $U$ decomposable or $0 \rightarrow  \mathcal{O} \rightarrow U \rightarrow \mathcal{O} \rightarrow 0 $ 
        \item $V$ is not semistable and $h^0 (L^{-2} \otimes \mathrm{det}(V) \otimes K ) > 1 $ 
        \item $V$ is not semistable and $h^0 (L^{-2} \otimes \mathrm{det}(V) \otimes K ) = 1 $ and $V = L\oplus (L^* \otimes \mathrm{det}(V) ) $
    \end{enumerate}

\end{proposition}

Suppose $V$ is not stable. 
Let $ L$ be the ( most ?) unstable subspace of $V$. 
Then
\begin{equation}
    0 \rightarrow  L \rightarrow  V \rightarrow  L^* \otimes \mathrm{det} V  \rightarrow  0 
\end{equation}

\begin{equation}
    0 \rightarrow  F \rightarrow  \mathrm{End} _0 ( V \otimes K) \rightarrow L^{-2} \otimes \mathrm{det} ( V) \otimes K \rightarrow  0 
\end{equation}

$H^0 ( L^{-2} \otimes \mathrm{Det} (V)  \otimes K ) = \mathrm{Hom} ( L...) $ 


$H^0 ( F) = H^0 ( \mathrm{End}_0 ( V) \otimes K ) $ 
if and only if $ V$ does not occur in a stable Higgs bundle. 

[[ EXPAND THIS END SECTION ]]


% section (end)



\bibliographystyle{plain}
\bibliography{}


\end{document} 

